Regression Cube Analysis of Cohort Study Data

### 2015-03-21 draft.tex
added Implementation subsec

\subsection{Implementation} \label{implementation}
\begin{figure}[htb]
 \centering
 \includegraphics[width=2.8in]{figures/placeholder}
 \caption{
 \com{Describe the Bootstrap/Angular/D3 Frontend, Node backend, R/OCPU Backend.}
 }
  \label{fig:Implementation}
\end{figure}
%%
\com{Use VAST'14 as Guideline}
\com{Cloud computing}
\com{Volume Rendering vs Particles}
\com{Speed is merely a matter of available server machines due to parallelization process.}
\com{Security enabled by hashing files.}
\com{Bootstrap/Angular/D3 Frontend, Node backend, R/OCPU Backend (Fig.~\ref{fig:Implementation})}

>>>>

\subsection{Implementation} \label{implementation}
\begin{figure}[htb]
 \centering
 \includegraphics[width=2.8in]{figures/placeholder}
 \caption{
 \com{Describe the Bootstrap/Angular/D3 Frontend, Node backend, R/OCPU Backend.}
 }
  \label{fig:Implementation}
\end{figure}
%%
Relying on web technologies paid off in previous collaboration with our clinical exerts, since it allows for:
\begin{itemize}
	\item easy exchange of software, without the need of installing anything other than a modern web browser,
	\item fast iterative adaption of method changes, without the need of installing updates,
	\item outsourcing computation-heavy tasks to server-clusters, which do not have to be in local proximity.
\end{itemize}
%%
The ongoing transition of open-science software into the web spawned numerous projects, making state-of-the-art algorithms available in this domain.
%%
\paragraph{Front-End.}
%%
The front end is created using \texttt{HTML5}, \texttt{CSS3} and \texttt{Javascript}.
%%
\texttt{Angular.js}\footnote{Open Source; Maintained by Google, \href{https://www.angularjs.org/}{\texttt{www.angularjs.org}}} abstracts web application into models and views, allowing for a responsive way to combine \texttt{HTML} and \texttt{Javascript}.
%%
\texttt{Angular.js} is forcing developers to write modularized code, which makes the components easier expandable while keeping the code maintainable by including unit tests.
%%
The page layout is handled using \texttt{Twitter Bootstrap}\footnote{Open Source; Maintained by Twitter, \href{http://getbootstrap.com}{\texttt{getbootstrap.com}}}, which also provides a rich set of UI elements with proper stylings.
%%
The 2D mosaic plot is implemented using \texttt{Data driven Documents}(\texttt{D3.js}), which is very popular in information visualization using vector graphics \cite{D3}.
%%
It provides fast and easy methods for binding data to graphical elements.
%%
The 3D plot is created using the WebGL-based \texttt{Threejs}\footnote{Open Source; Originally developed by R. Cabello, \href{http://threejs.org}{\texttt{threejs.org}}} library.
%%
We experimented with different ways for achieving the cube representation, including volume rendering, cube primitives for each data point and shader-based solutions.
%%
Proper open source volume rendering methods are not available for the web, the effort of writing one from scratch was not worth the counter value.
%%
Creating a cube primitive for each data point resulted in non-interactive frame-rates for data sets larger than 30 features (creating 30$^3$ cube primitives).
%%
We use a shader-based solution by rendering the cube as a sprite based particle system, allowing to customize color and opacity of every data point.
%%
It also is the fastest solution that we tested.

\paragraph{Back-End.}
Two server structures serve as back-end.
%%
The first one is the web-server, which is written in \texttt{Javascript} using \texttt{NodeJS}\footnote{Open Source; Maintained by Joyent Inc, \href{http://nodejs.org}{\texttt{nodejs.org}}}, running on Googles V8 Javascript runtime environment.
%%
It is hosted on \texttt{Heroku}\footnote{Owned by Salesforce.com, \href{https://www.heroku.com/}{\texttt{heroku.com}}}, a cloud application platform.
%%

The statistical processors yield the second structure.
%%
They rely on the statistical programming language \texttt{R}\footnote{Open Source; \href{http://r-project.org}{\texttt{r-project.org}}}.
%%
It is widely adopted in the statistical analysis community, yielding a rich support of fast state-of-the-art statistics algorithms as well newly published methods.
%%
\texttt{OpenCPU} is a \texttt{R} package and provides a API for accessing it via HTTP calls.
%%
This way, any computer, which runs \texttt{R} can be turned into a statistical processor for our project.
%%
The backend functions necessary for all cube calculations are provided via an \texttt{R} package.
%%
It uses multi-core optimization to use all machine CPUs to speed up the calculation process.
%%
The server workload balances are managed by the front-end code.

\paragraph{Access and Source.}
%%
A running instance of the \emph{Regression Cube} prototype can be found under \href{http://regressioncube.herokuapp.com/}{\texttt{regressioncube.herokuapp.com}}.
%%
The source for the prototype is freely available at \texttt{Github}.
%%
Instructions and code on how to create a setup running the \emph{Regression Cube} statistical backend through a \texttt{Ubuntu} server using \texttt{OpenCPU} can be found here: \href{https://github.com/paulklemm/regression-cube-r-package}{\texttt{github.com/paulklemm/regression-cube-r-package}}.
%%
The front-end source as well as the \texttt{Nodejs} backend can be found here: \href{https://github.com/paulklemm/regression-cube-prototype}{\texttt{github.com/paulklemm/regression-cube-prototype}}.
%%
Using \href{https://www.heroku.com/}{\texttt{www.heroku.com}}, the front-end setup is as easy as cloning the repository into a Heroku homepage. 
%%
% \com{Use VAST'14 as Guideline}
% \com{Cloud computing}
% \com{Volume Rendering vs Particles}
% \com{Speed is merely a matter of available server machines due to parallelization process.}
% \com{Security enabled by hashing files.}
% \com{Bootstrap/Angular/D3 Frontend, Node backend, R/OCPU Backend (Fig.~\ref{fig:Implementation})}
